\chapter*{Abstract}
\thispagestyle{empty}

% Problem addressed
The agricultural sector faces increasing challenges in maintaining efficiency and sustainability in small-scale farming environments. Urban and small-scale farmers struggle with limited space utilization, inefficient resource management, and lack of automation in routine tasks.

% Proposed solution concept
This report presents the design of a FarmBot system, an automated agricultural solution that combines robotics and IoT technology to create an intelligent farming platform. The system provides precision control over planting, watering, and monitoring operations while optimizing resource usage.

% Main findings and outcomes
Our analysis reveals strong market demand for automated farming solutions, particularly in urban and small-scale settings. The technical requirements and system architecture have been defined, establishing a robust foundation for implementation. The proposed solution addresses key gaps in existing agricultural automation technologies.

% Objectives, methods, and anticipated impact
The project aims to develop a user-friendly, efficient farming automation system using modern software engineering methodologies. Methods include comprehensive market research, requirements engineering, and systematic system design using UML modeling. The anticipated impact includes improved farming efficiency, reduced resource wastage, and increased accessibility to urban farming solutions.

\textbf{Keywords:} Agricultural automation, precision farming, IoT, robotics, urban farming
